% TeX_root = ../main.tex

\chapter{}

\begin{example}
  Let $X$ be a vector space and let $f: X \to \mathbb{C}$ be a linear map. Define $\phi: X \to R^{+} := \phi(x) = |f(x)|$. Then $\phi$ is a seminorm.
\end{example}

\begin{remark}
  Let $X$ be a TVS and $A \subset X^{*}$. We denote by $ \sigma(X, A)$, the topology on $X$ defined by $A$. ( initial topology).
  Recall that $\sigma(X, A)$ is Hausdorff if and only if $A$ separate points of $X$.

  $\sigma(X, X^{*})$ is called the weak topology on $X$.
 
  Also recall that $X \hookrightarrow X^{**}$ by the evaluation maps. Hence we can view $X$ as a subset $X^{**}$. And with this identification, we call $\sigma(X^{*}, X)$ the weak $*$ topology on $X^{*}$

\end{remark}

\begin{definition}
  Let $S$ be any set. Let $I$ be a directed set. A net in $S$ indexed by $\Lambda$ is a function $f:\Lambda \to S$. We denote the net by $(x_\lambda)_{\lambda \in \Lambda}$. 

  In addition if $S$ is a topological space, we say a net $(x_\lambda)_{\lambda \in \Lambda}$ converges to a point $x \in S$ if  for all open set $U$ in $S$ with $x \in U$, there exists an $\lambda_0 \in \Lambda$ such that for all $\lambda \ge \lambda_0$ we have $x_\lambda \in U$.
\end{definition}

\textcolor{red}{See how nets generalize the sequences to topological spaces from the metric space. For example, consider the definition of closedness in a metric space and a topological space. Find what exact property of the metric space makes it enough to be indexed by a countable totally ordered set for openess.}

\begin{remark}
  By definition, a basis of open neighborhoods of a point $x_0 \in X$ in $\sigma(X, A)$ is given \[
    \bigcup_{\substack{p_1 , p_2 , \ldots , p_n \in A \\ \epsilon_1 , \epsilon_2 , \ldots , \epsilon_n > 0}}\bigcap_{i = 1}^{n} \{ z \in Z | p_k(z-x_0) < \epsilon_k \}
  \]

  So the basis in a weak topology is \[
    \bigcup_{f_1 , f_2 , \ldots , f_n \in X^{*} \ \epsilon_1 , \epsilon_2 , \ldots , \epsilon_n > 0}(x_0) = \{  z \in Z \Big| |f_k(z- x_0)|< \epsilon_k, \textrm{ for all } k = 1, 2, \ldots n \}
  \]
\end{remark}

\begin{example}
  Let $S$ be a topologicla space, $E \subset S$, $x_0 \in E^\prime$. Then there is a net $(x_\alpha) \subset E$ such that $x_\alpha \to x_0$.
\end{example}
\begin{proof}
  
\end{proof}

 \begin{example}
   Let $X = \ell^{1}$. Then $X^{*} = \ell^{\infty}$. Then the weak * topology on $\ell^{\infty}$ is given by the pointwise convergence of a net $(f_\alpha) \subset \ell^{\infty}$ converges to $f \in \ell^{\infty}$ if and only if $f_\alpha(n) \to f(n)$ for all $ n \in \mathbb{N}$
 \end{example}
